Evaluating the Supportive Effect of Feature Selection Methods on Machine Learning Models in Monitoring Forest Health Using Hyperspectral Remote Sensing Data

### 2020-04-06 docs/00-manuscripts/ieee/ieee-manuscript.tex
AB-review: wording

% filter vs. no filter
% - Substantial effect for XGBoost and RF
% - SVM unaffected
When comparing the usage of filters against using no filter at all, there was only one instance (XGBoost on the NRI task) when the model without filtering showed a slighly better performance than the best filtered one (\autoref{fig:filter-effects-no-filter}).
For SVM, all filters and 'no filter' achieved the same performance on tasks VI and NRI even though \autoref{fig:fig:perf-result} lists "No Filter" as the best option.

@@

The most important features of each dataset showed an average decrease in RMSE of 1.57 (HR, B69) and 1.79 (VI, Vogelmann2) (\autoref{fig:fi-permut-vi-hr}).
For both datasets most features among the ten most important ones cluster around a wavelength range of 700 nm - 750 nm (the so called "red-edge").
For feature set HR four features in the infrared region (920 nm - 1000 nm) were identified by the model to be most important (causing a mean decrease in RMSE of around one percentage point).
Overall, most features show only a small importance with average decreases in RMSE below 0.5.

>>>>

% filter vs. no filter
% - Substantial effect for XGBoost and RF
% - SVM unaffected
When comparing the usage of filters against using no filter at all, there was only one instance (XGBoost on the NRI task) when the model without filtering showed a slighly better performance than the best filtered one (\autoref{fig:filter-effects-no-filter}).
For SVM, all filters and 'no filter' achieved the same performance on tasks VI and NRI even though \autoref{fig:perf-result} lists "No Filter" as the best option.

@@

The most important features of each dataset showed an average decrease in RMSE of 1.57 p.p. (HR, B69) and 1.79 p.p (VI, Vogelmann2) (\autoref{fig:fi-permut-vi-hr}).
For both datasets most features among the ten most important ones cluster around a wavelength range of 700 nm - 750 nm (the so called "red-edge").
For feature set HR four features in the infrared region (920 nm - 1000 nm) were identified by the model to be most important (causing a mean decrease in RMSE of around one percentage point).
Overall, most features show only a small importance with average decreases in RMSE below 0.5.
